---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Katie Latack"
date: "8/26/2019"
output: 
  html_document: 
    fig_height: 8
    fig_width: 12
    highlight: tango
    theme: flatly
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1846 rows and 3 variables (columns). The variables in the data frame are dataset, x, and y.

### Exercise 2

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

The shape is a dinosaur.

### Exercise 3


```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()


```

The value of *r* for the star is roughly the same as the value of *r* for the dino

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4


```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))

```

The *r* value for the circle is about the same as the *r* value for the dino.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)
```{r}
ggplot(data= datasaurus_dozen, aes(x=x, y=y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol=3) +
  theme(legend.position= "none")

datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r= cor(x,y)) %>%
  print(13)
```
